### 2015-07-16 rscripts/data_review.Rmd
user clusters displayed similarly to location clusters

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales")
sapply(req.packages, require, character.only = T)
```

@@

```{r, echo=FALSE}
week.melt <- setkey(melt(weekly.dt, id.var = "location_id", variable.name = "event", value.name = "week"), location_id)[km.dt]
week.melt[, inc := ifelse(event == "creation", 1, -1)]
week.melt <- week.melt[,list(inc = sum(inc)), keyby=list(cluster, week) ]
# ggplot(week.totals[cluster==1]) + aes(x = week, y = agg, fill=factor(cluster), group=cluster) + geom_area(stat="hline")
week.melt.fill <- setkey(Reduce(function(left, right) {
  ul <- left[!(week %in% right[,unique(week)]), unique(week)]
  ur <- right[!(week %in% left[,unique(week)]), unique(week)]
  ulc <- left[,unique(cluster)]
  rbind(left, right, 
    data.table(week=ul, inc=0, cluster=right[,unique(cluster)]),
    data.table(week=rep(ur, times=length(ulc)), inc=0, cluster=rep(ulc, each=length(ur)))
  )
}, Map(function(clus) week.melt[cluster == clus], week.melt[,unique(cluster)])), cluster, week)
week.totals <- week.melt.fill[,list(agg = cumsum(inc), week), keyby=cluster]
clusorder <- week.totals[,list(mx=max(agg)),keyby=cluster][,cluster,keyby=mx]$cluster
week.totals$cluster <- factor(week.totals$cluster, levels=clusorder)
ggplot(week.totals) + aes(x = week, y = agg, fill=cluster, order=cluster) + geom_area(position="fill")
```

@@

user.clusters <- kmParse(comp.user.short, 5, key="user_id", refevent="usage")
censor.dt[user.clusters$clustering][,
  list(leave=max(logout_time), join=min(login_time)), by=list(user_id,cluster)
]

>>>>

```{r, echo=FALSE, include=FALSE}
req.packages <- c("data.table", "ggplot2", "reshape2", "grid", "scales")
need.pkgs <- req.packages[!sapply(req.packages, require, character.only = T)]
if (length(need.pkgs) != 0) install.packages(need.pkgs, dependencies = T)
```

@@

```{r, echo=FALSE}
week.melt <- setkey(melt(weekly.dt, id.var = "location_id", variable.name = "event", value.name = "week"), location_id)[km.dt]
week.melt[, inc := ifelse(event == "creation", 1, -1)]
week.melt <- week.melt[,list(inc = sum(inc)), keyby=list(cluster, week) ]
# ggplot(week.totals[cluster==1]) + aes(x = week, y = agg, fill=factor(cluster), group=cluster) + geom_area(stat="hline")
week.melt.fill <- setkey(Reduce(function(left, right) {
  ul <- left[!(week %in% right[,unique(week)]), unique(week)]
  ur <- right[!(week %in% left[,unique(week)]), unique(week)]
  ulc <- left[,unique(cluster)]
  temp <- rbind(left, right)
  if (length(ul) != 0) temp <- rbind(temp, data.table(week=ul, inc=0, cluster=right[,unique(cluster)]))
  if (length(ur) != 0) temp <- rbind(temp, data.table(week=rep(ur, times=length(ulc)), inc=0, cluster=rep(ulc, each=length(ur))))
  temp
}, Map(function(clus) week.melt[cluster == clus], week.melt[,unique(cluster)])), cluster, week)
week.totals <- week.melt.fill[,list(agg = cumsum(inc), week), keyby=cluster]
clusorder <- week.totals[,list(mx=max(agg)),keyby=cluster][,cluster,keyby=mx]$cluster
week.totals$cluster <- factor(week.totals$cluster, levels=clusorder)
ggplot(week.totals) + aes(x = week, y = agg, fill=cluster, order=cluster) + geom_area(position="fill")
```

@@

user.clusters <- kmParse(comp.user.short, 5, key="user_id", refevent="usage")
setkey(censor.dt, user_id)
user.melt <- melt(censor.dt[user.clusters$clustering][,
  list(leave=max(logout), join=min(login)), by=list(user_id, cluster)
], id.vars = c("user_id","cluster"), value.name = "time", variable.name = "event")

agg.dt <- user.melt[, 
  week := floor(time/60/60/24/7)
][,
  inc := ifelse(event == "leave",-1,1)
][,list(inc = sum(inc)),keyby=list(week, cluster)]

agg.fill <- setkey(Reduce(function(left, right) {
  ul <- left[!(week %in% right[,unique(week)]), unique(week)]
  ur <- right[!(week %in% left[,unique(week)]), unique(week)]
  ulc <- left[,unique(cluster)]
  temp <- rbind(left, right)
  if (length(ul) != 0) temp <- rbind(temp, data.table(week=ul, inc=0, cluster=right[,unique(cluster)]))
  if (length(ur) != 0) temp <- rbind(temp, data.table(week=rep(ur, times=length(ulc)), inc=0, cluster=rep(ulc, each=length(ur))))
  temp
}, Map(function(clus) agg.dt[cluster == clus], agg.dt[,unique(cluster)])), cluster, week)

agg.final <- agg.fill[,
  list(net = sum(inc), gain = sum(inc[inc > 0]), loss = sum(inc[inc < 0])),
  by=list(week, cluster)
][,
  list(net, gain, loss, cum=cumsum(net), week),
  keyby=cluster
]

ggplot(agg.final) + theme_bw() +
  aes(fill = factor(cluster), x = week, y = cum) + geom_area(position="fill") +
  ylab("prop. users by cluster") + labs(fill="cluster") +
  coord_cartesian(xlim=c(34, 300), ylim=c(0,1))
